Relating games of Menger, countable fan tightness, and selective separability

### 2018-03-27 articles/relating-games-menger-cft-ss/article.tex
add bella notes

\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36606}
\email{steven.clontz@gmail.com}

@@

@@

>>>>

\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36688}
\email{sclontz@southalabama.edu}

@@

At this point, it's worth noting the following open question asked by Angelo Bella
in personal correspondance with the author. The following
term is defined in \cite{MR0370506}.

\begin{definition}
  A space is \term{dense-separable} if every dense subspace is separable.
\end{definition}

In dense-separable spaces, it is safe to assume the first player
only chooses countable dense subsets in the \(SS\) and \(CDFT\)
principles/games.

\begin{question}
  Suppose \(X\) is a dense-separable space such that every countable dense
  subspace \(D\subseteq X\) is \(SS^+\). Is \(X\) itself \(SS^+\)?
\end{question}

Bella noted that this is certainly true for non-strategic \(SS\),
as verified below. Note the use of knowledge of all \(D_n\) 
to define \(E_n\) in this proof,
demonstrating why it cannot be trivially modified to the \(SS^+\) case.

\begin{proposition}
  Let \(X\) be a dense-separable space such that every countable dense
  subspace \(D\subseteq X\) is \(SS\). Then \(X\) is \(SS\).
\end{proposition}

\begin{proof}
  Take \(\{D_n:n<\omega\}\) with \(D_n\subseteq X\) countable dense,
  so \(E_n=\bigcup\{D_m:n\leq m<\omega\}\) is countable dense in
  the \(SS\) subspace \(D=\bigcup\{D_n:n<\omega\}\). So choose \(F_n\in[E_n]^{<\omega}\)
  with \(cl_D(\bigcup\{F_n:n<\omega\})=D\) and therefore 
  \(cl(\bigcup\{F_n:n<\omega\})=X\).

  Define \(G_n\in[D_n]^{<\omega}\) by \(G_n=D_n\cap\bigcup\{F_m:m\leq n\}\).
  The result follows as \(\bigcup\{G_n:n<\omega\}=\bigcup\{F_n:n<\omega\}\).
\end{proof}

@@

\begin{corollary}
  The following are equivalent for any \(T_{3\frac{1}{2}}\)
  topological space \(X\).
    \begin{itemize}
      \item \(X\) is \(M^+\)
      \item \(X\) is \(\Omega M^+\)
      \item \(C_p(X)\) is \(CFT^+\)
      \item \(C_p(X)\) is \(CDFT^+\)
    \end{itemize}
\end{corollary}
